A Java Wrapper For Embarrassingly Parallel Problems

### 2013-11-26 paper/paper.tex
New figures

\documentclass[12pt]{article} 
\usepackage{graphics}
\usepackage{setspace}
\usepackage{cite}

@@

%TODO: Embarrassingly parallel diagram
\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
\caption{UML for the embarrassingly parallel framework}
\label{fig:uml}
\end{figure}

@@

Amazon also offers another service called Amazon Elastic MapReduce. This
combines its virtual instance framework with Apache Hadoop. As seen
in figure X, Hadoop breaks down the input data into parts, runs them in parallel
with the 'Map' function and then combines the results with the 'Reduce'
function. Dryad is a framework developed released by Microsoft Research that
allows the end-user to create directed acyclic computation graphs that run on
Windows High Performance Computer(HPC) clusters. Gunarathne et al. compared
the services using several applications to analyze performance, cost and
usability..

%TODO: Hadoop figure
\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
\caption{UML for the embarrassingly parallel framework}
\label{fig:uml}
\end{figure}

@@

\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{experiment/out.png}}}
\caption{Runtimes for the Ka/Ks Calculator though the framework}
\label{fig:graph}
\end{figure}

Figure 2 summarized the results; each line shows the time taken for each chunk
of the data. As the numbers of threads increases, the runtime of the program
decreases exponentially. In a few cases, there was an increase in time when
attempting to max out the CPU usage. This occurs because the framework has to
wait for the CPU to be finished with its previous work before it can start any
further jobs.

>>>>

\documentclass[12pt]{article} 
\usepackage{graphics}
\usepackage{setspace}
\usepackage{cite}
\usepackage{wrapfig}

@@

\begin{wrapfigure}{R}{0.5\textwidth}
    \begin{center}
        \includegraphics{figures/ep.jpg}
    \end{center}
    \caption{Embarrassingly Parallel Model}
    \label{fig:ep}
\end{wrapfigure}

@@

Amazon also offers another service called Amazon Elastic MapReduce. This
combines its virtual instance framework with Apache Hadoop. As seen
in figure \ref{fig:map}, Hadoop breaks down the input data into parts, runs them in parallel
with the 'Map' function and then combines the results with the 'Reduce'
function. Dryad is a framework developed released by Microsoft Research that
allows the end-user to create directed acyclic computation graphs that run on
Windows High Performance Computer(HPC) clusters. Gunarathne et al. compared
the services using several applications to analyze performance, cost and
usability.

\begin{wrapfigure}{L}{0.5\textwidth}
    \begin{center}
        \includegraphics{figures/MapReduce.jpg}
    \end{center}
    \caption{MapReduce Model}
    \label{fig:map}
\end{wrapfigure}

@@

\begin{figure}
{\resizebox{5.2in}{!}{\includegraphics{experiment/out.png}}}
\caption{Runtimes for the Ka/Ks Calculator though the framework}
\label{fig:kaksgraph}
\end{figure}

Figure \ref{fig:kaksgraph} summarized the results; each line shows the time taken for each chunk
of the data. As the numbers of threads increases, the runtime of the program
decreases exponentially. In a few cases, there was an increase in time when
attempting to max out the CPU usage. This occurs because the framework has to
wait for the CPU to be finished with its previous work before it can start any
further jobs.
